Exploring and Reverse Engineering the Motives Behind API Modifications

### 2015-03-27 rmtw/a6/latex8.tex
Updated data anal

The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}. More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{lientz1980software} the motive of the change corresponded to. Secondly, the codes were analysed from a high-level point of view, and the main goal was to identify trends in the codes. The third step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.

@@

>>>>

The analysis of the code and documentation was performed using grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.

More specifically, the approach undertaken was divided into three steps where the data was first coded based on which category of maintenance \cite{chapin2001types} the motive of the change corresponded to. The data were then mapped and coded to the laws presented by (!!!). The codes were then analysed from a high-level point of view, the main goal of which was to identify trends in the codes. The final step involved analysis of these trends, and it was during this stage the hypotheses were generated and formulated.

@@

A combination of the analysis between the changes to APIs, Lehmans laws and the software evolution categories \cite{chapin2001types} (!!!cites) allowed us to answer RQ1. The ability to answer RQ1 was the basis upon which we determined the answer to RQ2.
